Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-03 R0V0.tex
Add the information that \Delta_x is computed along signals

\mypara Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$, $(x,u)\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.

>>>>

\mypara Similarly to \eqref{eq:general system}, given a control $\delta_u$ for system \eqref{eq:general system:differential}, the solution to \eqref{eq:general system:differential} computed at time $t\geq0$, along signals $(x(t),u(t))\in\mathbb{R}^n\times\mathbb{R}^n$ and issuing from the  initial condition $\delta_x\in\mathbb{R}^n$ is denoted by $\Delta_x(t,x,\delta_x,u,\delta_u)$.
